Lemma 1

### 2021-03-04 notes/jessie-russian-lemma.tex
Updating dir deriv statement

\begin{lemma}
	For any $z \in \reals^d$, there exists a $v \in \E_p \partial L(u,Y)$ such that $\inprod{z}{v} = \E_p L'(u,Y;z)$.
\end{lemma}
\begin{proof}
	\jessie{Meeting notes: - Life will be easier if you forgot/redefined expected value of the subgradient -Want $Q_z$ to be subgradients, and get the everywhere selection - Careful about pulling out expectation in bullet 2; when is inner product of RV = expectation of inner product? - Point out contradicting the second line would yield contradiction of subgradient inequality - Argue $Q_z$ is measurable - Go slowly through the definition of measurable}

Fix $z$.
Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{V \in \V_u: \inprod{z}{V(\omega)} = L'(u,\omega;z) \}$.
Now, we want to take a measurable function $V \in \V_u$ that is a selection of $Q_z$ satisfying the following conditions:
\begin{enumerate}
	\item $V \in \V_u$.
	\item $\E_p V \in \E_p \partial L(u,Y)$.
	\item $\inprod{z}{\E_p V} = \E_p L'(u,Y,z)$
\end{enumerate} 
If these are true, then we can take $v := \E_p V$ and observe the result.

@@

1.  
If $Q_z$ is measurable and closed-valued, then by \jessie{Rockafellar VA 14.6}, we have a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
Thus, it just remains to show $Q_z$ is measurable and closed-valued.
First, we have $Q_z$ closed-valued by definition \jessie{Being lazy; will fill in later.}
%Now, we have $Q_z$ measurable if, for every open set $O \subset \reals^d$, the set $Q_z^{-1}(O) \in \B(\reals^d)$.
%\jessie{Rockafellar Wets VA Def 14.1}.
As measurable functions are closed under (countable) intersections, we have that $Q_z$ is the intersection of subgradients of $L$ and functions where the subgradient equals the directional derivative.
$V \in \V_u$ is measurable by definition.
Moreover, the function $\omega \mapsto \partial L(u,\omega)$ is measurable by \jessie{Rockafellar: Measurable Dependence, Corollary 4.6}, which also ensures $Q_z(\omega) \neq \emptyset$ for any $\omega \in \Omega$.
Now, we aim to show the set $\{c \in \reals^d: \inprod{z}{c} = L'(u,\omega;z)\}$ is measurable; as $L'$ is measurable and $\inprod{z}{\cdot}$ is continuous in its second argument, so the set is measurable. \jessie{Copying Russian argument}

As $Q_z$ is the intersection of these three sets, we conclude $Q_z$ is measurable and closed-valued, and therefore has a measurable selection $V \in \V_u$.

>>>>

\begin{lemma}
	For any $z \in \reals^d$, there exists a $v \in \E_p \partial L(u,Y)$ such that $\inprod{z}{v} = \E_p L'(u,Y;z)$.
\end{lemma}
\begin{proof}
	\jessie{Meeting notes: - Careful about pulling out expectation in bullet 2; when is inner product of RV = expectation of inner product? - Point out contradicting the second line would yield contradiction of subgradient inequality - Go slowly through the definition of measurable}

Fix $z$.
Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{V \in \V_u: \inprod{z}{V(\omega)} = L'(u,\omega;z) \}$. \jessie{type check!}
Now, we want to take a measurable function $V \in \V_u$ that is a selection of $Q_z$ satisfying the following conditions:
\begin{enumerate}
	\item $V \in \V_u$.
	\item $\E_p V \in \E_p \partial L(u,Y)$.
	\item $\inprod{z}{\E_p V} = \E_p L'(u,Y,z)$
\end{enumerate} 
If these are true, then we can take $v := \E_p V$ and observe the result.

@@

1.  
If $Q_z$ is measurable and closed-valued, then by \jessie{Rockafellar VA 14.6}, we have a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.
Thus, it just remains to show $Q_z$ is measurable and closed-valued.
First, we have $Q_z$ closed-valued by \jessie{Being lazy; will fill in later.}
%Now, we have $Q_z$ measurable if, for every open set $O \subset \reals^d$, the set $Q_z^{-1}(O) \in \B(\reals^d)$.
%\jessie{Rockafellar Wets VA Def 14.1}.
As measurable functions are closed under (countable) intersections, we have that $Q_z$ intersection of measurable functions.
$V \in \V_u$ is measurable by definition.
Moreover, the function $\omega \mapsto \partial L(u,\omega)$ is measurable by \jessie{Rockafellar: Measurable Dependence, Corollary 4.6}, which also ensures $Q_z(\omega) \neq \emptyset$ for any $\omega \in \Omega$.
Now, we aim to show the function $\omega \mapsto \{c : \inprod{z}{c} = L'(u,\omega;z)\}$ is measurable, which follows from measurability of $L'$ and the fact $\inprod{z}{\cdot}$ is continuous in its second argument, the set is measurable. \jessie{Copying Russian argument}

As $Q_z$ is the intersection of these three functions, we conclude $Q_z$ is measurable and closed-valued, and therefore has a measurable selection $V \in \V_u$ such that $\inprod{z}{V(\omega) = L'(u,\omega;z)$ for all $\omega \in \Omega$.
